Mapping malaria in pre-elimination settings by sharing spatial information between incidence and prevalence datasets

### 2019-07-16 ms.tex
Fix priors to match code. Closes #22.

\title[Mapping malaria by sharing spatial information]{Mapping malaria in pre-elimination settings by sharing spatial information between incidence and prevalence datasets}
\author[Tim C.D. Lucas {\it et al.}]{Tim C.D. Lucas}
\address{Big Data Institute,
Oxford,
UK.}
\email{timcdlucas@gmail.com}
\author{Anita Nandi}
\address{Big Data Institute,
Oxford,
UK.}

@@

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 0.6\textwidth]{figures/sen_both_cv12_preds.png}}
\caption{\label{predobsmapsen}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}

@@

We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \citep{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \citep{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.

@@

We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > 0.3) = 0.0000001$. 
This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500 individuals) within the same raster pixel.
The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
Given that the error on a prevalence estimate with sample size greater than 500 is quite small, the iid effect needs to be able to explain this difference.

@@

We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
As the models are being fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e. biased) and therefore correlation metrics were misleading.
% Why not correlation
To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.

@@

>>>>

\title[Mapping malaria by sharing spatial information]{Mapping malaria in pre-elimination settings by sharing spatial information between incidence and prevalence datasets}
\author[Tim C.D. Lucas {\it et al.}]{Tim C.D. Lucas}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\email{timcdlucas@gmail.com}
\author{Anita Nandi}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Michele Nguyen}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Susan Rumisha}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Rosalind Howes}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Katherine E. Battle}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Penelope Hancock}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Andre Python}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Ewan Cameron}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Pete Gething}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}
\author{Daniel J. Weiss}
\address{Big Data Institute,
University of Oxford,
Oxford,
UK.}

@@

\begin{figure}
% to be removed before submission
\makebox{\includegraphics[width = 1.1\textwidth]{figures/sen_both_cv12_preds.png}}
\caption{\label{predobsmapsen}
Incidence data and predicted incidence maps.
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially cross-validated out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially cross-validated out-of-sample polygons (bottom) for Senegal.
}

@@

We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \citep{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > \xi) = 0.00001$.
We used different $\zeta$  and $\xi$ values for each country: Indonesia $\zeta = 3, \xi = 1$, Senegal $\zeta = 1, \xi = 0.5$ and Madagascar $\zeta = 1, \xi = 1$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \citep{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.
As Senegal has a lower range of incidences in the data we set $\xi$ to a smaller value for this country.

@@

We assigned $\sigma_w$ a penalised complexity prior such that $P(\sigma_w > \phi) = 0.0000001$. 
This was chosen by finding the maximum difference in prevalence between point-surveys (with a sample size greater than 500 individuals) within the same raster pixel.
The differences between points within the same pixel can only be accounted for by the binomial error and this iid effect.
Given that the error on a prevalence estimate with sample size greater than 500 is quite small, the iid effect needs to be able to explain this difference.
In Senegal and Madagascar this value was relatively small so we set $\phi = 0.05$. 
In Indonesia however, there are many prevalence surveys in small areas and there is large differences in estimated prevalence within the same pixel.
Therefore we set $\phi = 0.3$.

@@

We considered the ability to predict polygon incidence correctly our main objective and our performance metric was mean absolute error (MAE).
As the models are being fitted on data on different scales we found that observations and predictions were sometimes correlated but shifted from the one-one line (i.e. biased) and therefore correlation metrics were misleading.
% Why not correlation
To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.
%Finally, we fitted each model to the full data set and examine the parameter estimates for these models.

@@

%\subsection{Parameter estimates}
% We can examine the parameters in the models fitted
% discuss beta for prev go
% discuss alpha 
% are other betas the same across models and countries.
